Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
...

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Although intelligent text search algorithms are widely available
  these days, documents are still hard to find in many cases. It is
  usually hard to find useful information in help systems and manual
  pages, even when required information exists in the documents.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \caption{Asking the help application on Mac how to remove a file.}
  \Description{Mac Mac}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \caption{Mac}
  \Description{Mac Mac}
\end{figure}

@@

The vocabulary problem and the translation problem can sometimes be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}'',
and simple query expansion is possible if a good thesaurus is available.

@@

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know the meaning of an icon on the desktop, he might think
``What is the symbol with curved lines and a circle
\includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
at the top of my Mac display?'',
but he cannot finding the information using these keywords in his brain.
(folding fan, two black 90-degree arcs above a black circle)

@@

% [[ExpandSearchの実例]]
%  まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
% [[実例1]] ExpandHelpの実際の利用
%  ScrapboxというWiki上にいろんな表現を用意しておく
%  Helpfeel
%   PayPayフリマなどですごく効率があがった
%  実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
% [[実例2]] 検索インタフェースの融合
%  マイHelpfeel
%  検索をひとつの方法に統合する
%   検索方法が複数だと面倒臭い
%    ググって出なければ逆引き辞典を検索する、みたいなのは面倒
%   同じ検索インタフェースでいろんなところを探すほうが簡単である
%   どこにメモしたか忘れて困ることがなくなる
%  自分のデータが増えていく状況のグラフを書ける!
% 
% [[実例3]]
%  gitのヘルプ - コマンドラインで動くもの
%   パラメタを指定して実行につなげることすらできる

@@

Some Unix command line tools have many options and features that are difficult to remember.
Many programmers are recently using the git version control system,
but the concept of git is difficult, and
the command line options are extremely complicated.
The total number of git manuals on unix is xxxxx lines.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Although intelligent text search algorithms are widely available
  these days, searching documents is still difficult in many cases.
  It is
  usually hard to find useful information in help systems and manual
  pages, even when required information exists in the documents.

@@

\begin{figure}[H]
  %\centering
  % \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}
  % \includegraphics[width=7cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \includegraphics[width=7cm,bb=-50 0 950 800]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
  \par
  (a) Searching ``remove files'' \hspace{3cm} (b) Searching ``Set clock''
  \caption{Asking the help application on Mac how to remove a file.}
  %\Description{Mac Mac}
\end{figure}

@@

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=12cm,bb=0 0 1310 1090]{figures/0cd679128d8f69eb2a8a966d6466a8a4.png}
%   \caption{Mac}
%   \Description{Mac Mac}
% \end{figure}

@@

The vocabulary problem and the translation problem can sometimes be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
},
and simple query expansion is possible if a good thesaurus is available.

@@

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know the meaning of an icon on the desktop, he might think
``What is the symbol with curved lines and a circle
\includegraphics[width=6mm,bb=-40 30 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
at the top of my Mac display?'',
but he cannot finding the information using these keywords in his brain.
(folding fan, two black 90-degree arcs above a black circle)

@@

In this section, we describe how
document expansion strategy based on {\ES} works in various environments.

%  まず実例を紹介する。実装はあとで。[[評価実験にもなっている。]]
% [[実例1]] ExpandHelpの実際の利用
%  ScrapboxというWiki上にいろんな表現を用意しておく
%  Helpfeel
%   PayPayフリマなどですごく効率があがった
%  実際これによりヘルプ問い合わせは劇的に減る (出典: Helpfeel)
% [[実例2]] 検索インタフェースの融合
%  マイHelpfeel
%  検索をひとつの方法に統合する
%   検索方法が複数だと面倒臭い
%    ググって出なければ逆引き辞典を検索する、みたいなのは面倒
%   同じ検索インタフェースでいろんなところを探すほうが簡単である
%   どこにメモしたか忘れて困ることがなくなる
%  自分のデータが増えていく状況のグラフを書ける!
% 
% [[実例3]]
%  gitのヘルプ - コマンドラインで動くもの
%   パラメタを指定して実行につなげることすらできる

@@

Unix command line tools usually have many options and features that are difficult to
understand and remember.
Many programmers are recently using the git version control system,
but the concept of git is difficult, and
the command line options are extremely complicated.
The total number of git manuals on unix is xxxxx lines.
